Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2019-05-06 Manuscript/manuscript.tex
Added missing citation, fixed some latex related problems.

\subsection{Measurements of acyl chain order parameters}
A R-type Proton Detected Local Field (R-PDLF) experiment was performed to determine C--H bond order
parameters
\begin{equation}\label{OPequation}
  S_{\rm{CH}}=\frac{1}{2}\langle3\cos^2\theta-1\rangle,
\end{equation}
  where $\theta$ denotes the angle of the C--H bond
with the bilayer normal and the angular brackets define a time average on a time scale of approximately 1 microsecond.
The experiment was done using a Bruker Avance III 400 spectrometer operating at a 1H Larmor frequency of 400.03 MHz
equipped with a standard 4 mm CP-MAS HXY probe. The set up of the R-PDLF experiment was the following
(using the notation from figures 1c and 2c in the original publication describing the R-PDLF experiment \cite{dvinskikh04}).
The magic angle spinning (MAS) frequency used was 5.15 kHz. The recoupling pulses in the R18 blocks had
therefore a length of 10.79 us which correspond to a nutation frequency of 46.35 kHz. Increments of 18x2 recoupling
pulses where used giving a spectral width of 2.6 kHz in the indirect dimension and a total number of 32 points in
the indirect dimension were recorded. These settings enable to record dipolar slices with a C--H bond order parameter
resolution of +- 0.01. The C--H bond order parameter determined from a given dipolar
splitting, $\Delta\nu$ (see e.g. Fig. \ref{R-PDLFslices} in SI)
is equal to $\Delta\nu/(0.315\times21.5 kHz)$, where 0.315 is
the scaling factor of the R18 recoupling sequence and 21.5 kHz is the maximum $^1$H-$^{13}$C dipolar coupling for a C--H bond.
The refocused-INEPT transfer \cite{morris79,burum80} %[G. Morris and R. Freeman, J. Am. Chem. Soc. 101, 760 (1979);
\todo{ I could not find this reference [D. Burum, R. Ernst, J. Mag. Res. 39, 163 (1980)]}
was used for transferring the polarization from $^1$H nuclei to the covalently bond $^{13}$C nuclei with the delays $\tau_1$ = 1.94 ms and $\tau_2$ = 0.97 ms
(set as multiples of the MAS rotation period). The pulses for the refocused-INEPT sequence had a nutation frequency equal to 63.45 kHz.
For acquiring the spectra, a total number of 1024 transients were recorded for each point in the indirect dimension, using an acquisition
time of 0.1 s under SPINAL64 $^1$H decoupling \cite{fung00} with a nutation frequency of 50 kHz, and with dwell time giving a spectral
width of 200 ppm for the $^{13}$C chemical shift dimension. The set of free induction decays recorded were then processed as
described e.g. in Ref. \citenum{ferreira08}. The dipolar splittings in the crowded spectral region
between 29 and 30 ppm were assigned based on the previous assignments for POPC \cite{ferreira13} 
and the POPS order parameters calculated from simulations in this work.

@@

\begin{figure}[tb!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/ecc_pops/Order-parameters_form-factors_exp-L17-ECC-lipids.pdf}
  \includegraphics[width=\figwidth]{../img/ecc_pops/pops_chemfig.pdf} 
\hfill
  \caption{\label{simVSexpNOions_POPS} 
    \textbf{Top:} X-ray scattering form factors from simulations with Lipid17/Dang \citep{lipid17-future, dang2006} and 
    the ECC-POPS/ECC-ions \cite{martinek17, Pluhackova2016} compared with experiments~\citep{kucerka14} at 298~K. 
    \textbf{Middle:} Order parameters of POPS head group, glycerol backbone and acyl chains  
    from simulations with the Lipid17 \citep{lipid17-future} and the ECC-POPS models 
    compared with experiments at 298~K. \citep{NMRlipidsIV}
    Open/closed symbols are used for palmitoyl/oleoyl chains of POPS. 
    \textbf{Bottom:} The chemical structure of POPS and the labeling of the carbon segments. 
  }  
  \todo{J: flip the chemical structure so that it agrees with the left-to-right reading of the plot.} \\
  \todo{The experimental order parameters from sn-1 chain are missing from the figure.} \\
  \todo{Inverted axis and positive value as label would be more clear for the order parameter figure.}
\end{figure}

>>>>

\subsection{Measurements of acyl chain order parameters}
A R-type Proton Detected Local Field (R-PDLF) experiment was performed to determine C--H bond order
parameters
\begin{equation}\label{OPequation}
  S_{\rm{CH}}=\frac{1}{2}\langle3\cos^2\theta-1\rangle,
\end{equation}
  where $\theta$ denotes the angle of the C--H bond
with the bilayer normal and the angular brackets define a time average on a time scale of approximately 1 microsecond.
The experiment was done using a Bruker Avance III 400 spectrometer operating at a 1H Larmor frequency of 400.03 MHz
equipped with a standard 4 mm CP-MAS HXY probe. The set up of the R-PDLF experiment was the following
(using the notation from figures 1c and 2c in the original publication describing the R-PDLF experiment \cite{dvinskikh04}).
The magic angle spinning (MAS) frequency used was 5.15 kHz. The recoupling pulses in the R18 blocks had
therefore a length of 10.79 us which correspond to a nutation frequency of 46.35 kHz. Increments of 18x2 recoupling
pulses where used giving a spectral width of 2.6 kHz in the indirect dimension and a total number of 32 points in
the indirect dimension were recorded. These settings enable to record dipolar slices with a C--H bond order parameter
resolution of $\pm 0.01$. The C--H bond order parameter determined from a given dipolar
splitting, $\Delta \nu$ (see e.g. Fig. \ref{R-PDLFslices} in SI)
is equal to $\Delta \nu / (0.315 \times 21.5 \mathrm{kHz})$, where 0.315 is
the scaling factor of the R18 recoupling sequence and 21.5 kHz is the maximum $^1$H-$^{13}$C dipolar coupling for a C--H bond.
The refocused-INEPT transfer \cite{morris79,burum80} %[G. Morris and R. Freeman, J. Am. Chem. Soc. 101, 760 (1979);
was used for transferring the polarization from $^1$H nuclei to the covalently bond $^{13}$C nuclei with the delays $\tau_1$ = 1.94 ms and $\tau_2$ = 0.97 ms
(set as multiples of the MAS rotation period). The pulses for the refocused-INEPT sequence had a nutation frequency equal to 63.45 kHz.
For acquiring the spectra, a total number of 1024 transients were recorded for each point in the indirect dimension, using an acquisition
time of 0.1 s under SPINAL64 $^1$H decoupling \cite{fung00} with a nutation frequency of 50 kHz, and with dwell time giving a spectral
width of 200 ppm for the $^{13}$C chemical shift dimension. The set of free induction decays recorded were then processed as
described e.g. in Ref. \citenum{ferreira08}. The dipolar splittings in the crowded spectral region
between 29 and 30 ppm were assigned based on the previous assignments for POPC \cite{ferreira13} 
and the POPS order parameters calculated from simulations in this work.

@@

\begin{figure}[tb!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/ecc_pops/Order-parameters_form-factors_exp-L17-ECC-lipids.pdf}
  \includegraphics[width=\figwidth]{../img/ecc_pops/pops_chemfig.pdf} 
\hfill
  \caption{\label{simVSexpNOions_POPS} 
    \textbf{Top:} X-ray scattering form factors from simulations with Lipid17/Dang \citep{lipid17-future, dang2006} and 
    the ECC-POPS/ECC-ions \cite{martinek17, Pluhackova2016} compared with experiments~\citep{kucerka14} at 298~K. 
    \textbf{Middle:} Order parameters of POPS head group, glycerol backbone and acyl chains  
    from simulations with the Lipid17 \citep{lipid17-future} and the ECC-POPS models 
    compared with experiments at 298~K. \citep{NMRlipidsIV}
    Open/closed symbols are used for palmitoyl/oleoyl chains of POPS. 
    \textbf{Bottom:} The chemical structure of POPS and the labeling of the carbon segments. 
  }  
  \todo{J: flip the chemical structure so that it agrees with the left-to-right reading of the plot.} \\
\end{figure}
